%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

% Create links
\usepackage{hyperref}

% Increase text height
\textheight=700pt

\usepackage[space]{xeCJK}

\title{Lucas Kjaero-Zhang Resume}

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Lucas Kj\ae{}r\o{}-Zhang}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{(619) 905-1772\\San Diego, CA}
\address{\href{mailto:lucas@lucaskjaerozhang.com}{Lucas@LucasKjaeroZhang.com}\\\href{https://www.lucaskjaerozhang.com}{www.LucasKjaeroZhang.com}}

% Uncomment to add a third address

%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{\textbf{Amazon}}
\location{San Diego, CA}
\dates{2020-Present}
\title{\textbf{Software Engineer II - Fire TV}}
\begin{position}
Owned and performed rollout of Fire TV screensaver ads to Germany, Japan, and the United Kingdom. Expanded screensaver monitoring to build confidence in the international launch. Primary technical designer for deep linking project that installs apps (eg Disney+) and loads content when users click on ads. 
\end{position}

\employer{\textbf{Intuit}}
\location{San Diego, CA}
\dates{2018-2020}
\title{\textbf{Software Engineer II}}
\begin{position}
Led a team of four engineers across two product groups to decommission a decades old tax workflow engine used by over 100 tax content developers, moving its capabilities to a newer tool in the same problem space. Migrated capabilities are used to assemble Turbotax weekly releases, determine whether a customer can file their taxes, and attribute revenue to different parts of the product.
\\
\\
Created data collection infrastructure and customer dashboard to allow stakeholders and senior leadership to analyze the automation level of the TurboTax release pipeline. Infrastructure used Amazon Kinesis and Elasticsearch, with React for displaying the data.
\\
\\
Maintained and expanded an internal continuous delivery tool used to perform all releases in the TurboTax ecosystem. Owned rolling out capability to automatically redeploy all services with the latest security patches.
\end{position}

\employer{\textbf{Intuit (Via Tek-Systems)}}
\location{San Diego, CA}
\dates{2017-2018}
\title{\textbf{Software Engineer in Quality}}
\begin{position}
Designed and expanded test suites for \href{https://www.freefilefillableforms.com}{Free File Fillable Forms}, including unit, service, UI, and performance tests as the project's sole quality engineer.
\end{position}

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}

\par
\textbf{Fluentlabs Reader (in progress)}:
A website to help language learners transition from textbooks to real text by giving them definitions and examples for whatever they want to read. React frontend with Python and Scala microservices managed by Kubernetes. Uses Elasticsearch for language content, and Terraform for infrastructure management. \textit{\href{https://github.com/fluent-labs/api}{Github}}\textit{\href{https://www.fluentlabs.io/}{www.fluentlabs.io}}

\par
\textbf{MNIST}:
Created a computer vision model to recognize handwritten digits with 99\% accuracy. Model ranked in the top 36\% globally of all Kaggle users. Used a Convolutional Neural Network implemented in TensorFlow. \textit{\href{https://github.com/lucaskjaero/MNIST}{Github}}

% \par
% \textbf{PyCasia}:
% Created a library to work with the open source CASIA chinese handwriting dataset, used to train computer vision algorithms to recognize handwritten text. The library has been starred on github at least 29 times, and has been successfully used to train an algorithm. \textit{\href{https://github.com/lucaskjaero/PyCasia}{Github}}

% \par
% \textbf{Chinese Vocabulary Finder}:
% Used open source libraries, and natural language processing algorithms to tokenize and find unfamiliar words in Chinese text to aid learning. \textit{\href{https://github.com/lucaskjaero/Chinese-Vocabulary-Finder}{Github}}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}

\textbf{Technologies (Many Work Projects)}:
\href{https://www.lucaskjaerozhang.com/technology/java/}{Java},
\href{https://www.lucaskjaerozhang.com/technology/python/}{Python},
\href{https://www.lucaskjaerozhang.com/technology/scala/}{Scala},
\href{https://www.lucaskjaerozhang.com/technology/spring-boot/}{Spring Boot},
\href{https://www.lucaskjaerozhang.com/technology/sql/}{SQL}.
\\
\textbf{Technologies (Some Work Projects)}:
Apache Spark,
\href{https://www.lucaskjaerozhang.com/technology/aws/}{AWS},
\href{https://www.lucaskjaerozhang.com/technology/docker/}{Docker},
\href{https://www.lucaskjaerozhang.com/technology/elasticsearch/}{Elasticsearch},
\href{https://www.lucaskjaerozhang.com/technology/gatling/}{Gatling},
\href{https://www.lucaskjaerozhang.com/technology/javascript/}{Javascript},
Jenkins,
\href{https://www.lucaskjaerozhang.com/technology/react/}{React},
\href{https://www.lucaskjaerozhang.com/technology/sklearn/}{Scikit-Learn},
Selenium,
Splunk.
\\
\textbf{Technologies (Side Projects)}:
Chef,
\href{https://www.lucaskjaerozhang.com/technology/django/}{Django},
Elixir,
\href{https://www.lucaskjaerozhang.com/technology/keras/}{Keras},
Kubernetes,
\href{https://www.lucaskjaerozhang.com/technology/pandas/}{Pandas},
Terraform.
\\
\textbf{Natural Languages}: Danish (Native - Heritage), English (Native), \href{https://www.lucaskjaerozhang.com/lucas-kjaero-zhang-%E4%B8%AA%E4%BA%BA%E7%AE%80%E5%8E%86.pdf}{Mandarin Chinese (Working Proficiency)}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Austin College}\hfill Sherman, TX\\
Bachelor of Arts, Cum Laude, May 2015\hfill Majors: Computer Science and Chinese\\
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	Honors
%-------------------------------------------------------------------------------
\section{HONORS}
Carnegie Mellon University - Heinz College ITLab Fellowship\hfill Summer 2014\\
Machine Learning Society - Blockchain Hackathon Winner\hfill Spring 2018

\end{resume}
\end{document}
